One of the major issues in the automotive industry is the constant growing complexity of E/E (Electrics/Electronics) systems and the thereof resulting fault propagation due to the strong interconnection of the systems. The area of \emph{functional safety} is concerned with the prevention of non tolerable risks in event of error. This is conducted by identifying possible hazards, estimating the potential risks and developing necessary countermeasures, based on these investigations. This process requires an accurate and thorough comprehension of the observed E/E system.

The service oriented architecture is a design paradigm, which focuses on the concept of software reuse by implementing functionalities as technology independent and loosely coupled services. Although this architectural style is already widely applied in web applications, it has not yet found its way into safety-critical embedded systems.

This Bachelor's thesis investigates the applicability of service oriented architectures for such systems, with a focus on \emph{functional safety} and \emph{fault tolerance} context. The first part of the thesis deals mainly with certain terms, which are crucial for the subsequent presented concepts, and investigates them with respect to embedded systems. On this basis it is defined what \emph{safety as a service} can mean in general, and how the actual implementation in a given safety-critical system may look like, in order to meant with the requirements specified in the \mbox{ISO 26262} standard. The \mbox{ISO 26262} standard is an international safety standard for safety-critical E/E systems in vehicles with a maximum gross weight of 3.500 kg.