\begin{thebibliography}{9}
\bibitem{versteeg}
Versteeg, H.K., and Malalasekera, W., \emph{An Introduction to COMPUTATIONAL FLUID DYNAMICS: The Finite Volume Method, 2nd ed.}, Pearson Education Limited, Harlow, England, 2007.

\bibitem{hassler}
Hassler, W., ``Numerische Berechnungsverfahren (CFD-Teil)'', 2012.

\bibitem{frohlich}
Fröhlich, J., \emph{Large Eddy Simulation turbulenter Strömungen, 1st ed.}, Teubner Verlag, Wiesbaden, 2006.

\bibitem{cerbe}
Cerbe, G., and Wilhelms, G., \emph{Technische Thermodynamik: Theoretische Grundlagen und praktische Anwendungen, 15th ed.}, Carl Hanser Verlag, München, 2008.

\bibitem{ochoa}
Ochoa, J.S., and Fueyo, N., ``Large Eddy Simulation of the flow past a square cylinder,'' Zaragoza, Spain.

\bibitem{anderson}
Anderson, D., and Tsao, J., ``Evaluation and Validation of the Messinger Freezing Fraction,'' Ohio Aerospace Institute, Brook Park, Ohio, 2003.

\bibitem{leap team}
LEAP CFD Team, ``Tips \& Tricks: Estimating the First Cell Height for correct Y+,'' [web site], URL: http://www.computationalfluiddynamics.com.au/tips-tricks-cfd-estimate-first-cell-height/ [cited 12 March 2015].

\bibitem{sas_ip}
SAS IP, Inc., ``Heat Transfer,'' [web site], URL: http://www.arc.vt.edu/ansys\_help/cfx\_\\mod/i1301427.html [cited 12 March 2015].

\bibitem{sas_ip2}
SAS IP, Inc., ``The Large Eddy Simulation Model (LES),'' [web site], URL: http://www.arc.vt.edu/ansys\_help/cfx\_\\mod/i1303019.html [cited 15 March 2015].

\bibitem{ansys}
ANSYS, Inc., ``ANSYS CFX-Solver Theory Guide,'', Southpointe, 2009.

\end{thebibliography}